Cyclist video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda

### 2024-04-22 paper.qmd
Wrap text

---
title: "Cyclist video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda"
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Cyclist video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda"
format: pdf
number-sections: true
bibliography: references.bib
editor:
  markdown: 
    wrap: sentence
---
